### 2021-10-05 README.Rmd
corrige read me

    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drakee_load_all()`.

>>>>

    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.
